---
title: "Getting Started with afterthoughts"
author: "Catalina Canizares"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Getting Started with afterthoughts}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Introduction

The `afterthoughts` package is designed to enhance the teaching and learning experience in R programming classrooms. It provides a structured approach to student reflection, ensuring that learners have the opportunity to process and internalize their learning experiences.

This vignette will guide you through the basic usage of the package and show you how to integrate reflection prompts into your teaching practice.

# Installation

You can install the package from GitHub using:

```{r eval = FALSE}
# install.packages("devtools")
devtools::install_github("ccani007/afterthoughts")
```

# Basic Usage

Here's how to use the main functions of the package:

```{r}
library(afterthoughts)

my_turn()
```

Each time a student runs the `my_turn()` function, they will receive a random reflection prompt.

Lets try it out:

```{r}
my_turn()
``` 


# Exploring Reflection Prompts

The `afterthoughts` package provides a collection of thoughtfully crafted reflection prompts. Let's explore how to use them:

## Viewing All Prompts

To see all available reflection prompts, use the `get_prompts()` function:

```{r}
library(afterthoughts)
get_prompts()
```


## Using Prompts Effectively

Here are some tips for using these prompts in your classroom:

1. **Daily Reflection**: Use a prompt at the end of each class to encourage students to process what they've learned

2. **Group Discussion**: Select a prompt for small group discussions about the day's material

3. **Writing Exercise**: Have students write responses to prompts as a homework assignment

4. **Class Warm-up**: Start class with a reflection on the previous session's learning

## Next Steps

- Try incorporating these prompts into your next R programming class

- Observe how students engage with the reflection process

- Adjust the prompts or create your own based on student responses

- Share your experiences with the teaching community

Remember, reflection is a powerful tool for deepening understanding and making learning more meaningful for your students.


